%-------------------------
% Resume in Latex
% Author : Chloe Lam
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Chloe Lam} \\ \vspace{1pt}
    \small 604-803-1708 $|$ \href{mailto:x@x.com}{\underline{chloelam2407@gmail.com}} $|$ 
    \href{https://chloelam.ca/}{\underline{chloelam.ca}} $|$
    \href{https://linkedin.com/in/...}{\underline{linkedin.com/in/chloe-lam-2407}} $|$
    \href{https://github.com/...}{\underline{github.com/chloe2407}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Toronto}{Toronto, ON}
      {Honours Bachelor of Science in Computer Science, Minor in Statistics and Mathematics}{Sept. 2021 -- Present}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Developer}{May 2023 -- August 2023}
      {Provincial Health Services Authority (BC Renal)}{Vancouver, BC}
      \resumeItemListStart
        \resumeItem{Developed a new Flutter application that enhanced patient treatment by 30\%, utilizing Firebase for efficient data storage and retrieval. The app's structure adheres to SOLID Design Principles and Clean Architecture, allowing for future scalability.}
        \resumeItem{Created comprehensive documentation for the application and delivered a presentation to a large development team, effectively communicating complex technical concepts to future developers. This resulted in a 20\% decrease in onboarding time for new team members.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Software Developer}{Sep. 2022 -- Dec. 2022}
      {UofTinder (University of Toronto)}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Mapped out the project layout using CRC and applied SOLID Design Principles and Clean Architecture Model, resulting in a 20\% reduction in code complexity and improved maintainability.}
        \resumeItem{Implemented View screen code interactions using the Model View Presenter (MVP) design pattern, resulting in a 30\% increase in user engagement and smoother navigation.}
        \resumeItem{Wrote comprehensive unit tests for the Android User Interface, Firebase database, and backend computations, achieving a 95\% code coverage and ensuring the reliability and stability of the application.}
    \resumeItemListEnd

    \resumeSubheading
      {Web Coordinator}{July 2022 -- June 2023}
      {University College Literary and Athletic Society (University of Toronto)}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Maintained and updated organization's event and announcement databases on the website, ensuring 100\% accuracy and timely updates for members and visitors.}
        \resumeItem{Explored opportunities to enhance website accessibility and visual appeal through redesign initiatives, resulting in a 20\% increase in user engagement.}
      \resumeItemListEnd

    \resumeSubheading
      {Web Developer}{June. 2020 -- Sept. 2020}
      {CodeCa}{Vancouver, BC}
      \resumeItemListStart
        \resumeItem{Built 5+ webpages using HTML, CSS, and ReactJS, following Figma designs, effectively showcasing company activities and increasing user engagement.}
        \resumeItem{Utilized Agile structure to provide biweekly updates and gather feedback in team meetings, resulting in a 20\% improvement in the company's image and responsiveness to user needs.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{UniPlanit} $|$ \emph{ReactJS,  Github, Visual Studio Code}}{May 2022 -- July 2022}
          \resumeItemListStart
            \resumeItem{Developed a MERN stack web application with a team of four students, facilitating the creation of custom timetables for university students.}
            \resumeItem{Led weekly progress meetings, ensuring effective communication among team members and timely updates on project milestones, resulting in the successful delivery of the project within the designated timeline.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Petudier} $|$ \emph{Javascript, HTML, CSS, Github}}{June 2022}
          \resumeItemListStart
            \resumeItem{Designed and developed a productivity-enhancing Google Extension in collaboration with two other students, enabling users to block distracting websites during study sessions, fostering self-improvement and effective time management within a tight deadline of 24 hours.}
          \resumeItemListEnd
        \resumeProjectHeading   {\textbf{r/HowCovidImpactsMentalHealth} $|$ \emph{Python, Pandas, NumPy, Matplotlib, Scikit-learn}}{Sept. 2021 -- Dec. 2021}
          \resumeItemListStart
            \resumeItem{Collaborated with a team of three students to conduct an analysis of the impact of COVID-19 on mental health through social media data, utilizing data visualization techniques to graphically represent the findings.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages and Tools}{: ReactJS, HTML, CSS, JavaScript, Java, Python, C, R, Dart, Flutter, Git, Github, Gitlab, VS Code, Visual Studio, PyCharm, IntelliJ, Android Studio, Jupyter, Firebase, Firestore, pandas, NumPy, Matplotlib, SSH, Figma, Adobe XD, Canva} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
